---
title: "dsc2BE_example.Rmd"
output: html_document
---

This document shows an example of the use of the function dsc2BE
which "converts" a dsc to a BatchExperiments registry so that you can
use the BatchExperiments pipeline to run the dsc on a cluster.

Note that as far as I can see the BatchExperiments pipeline does not
save everything that the dsc pipeline saves. Specifically the BE pipeline
only appears to save the final results of each method, which the way I have
set it up here is the score. In comparison dsc saves the data, output and score.

First I set up the DSC. 


```{r}
library("dscr")
library("BatchExperiments")

dsc_eg=new.dsc("one-sample-location","osl-files")

sourceDir("methods")
sourceDir("datamakers")
###### Add Scenarios #####

addScenario(dsc_eg,"normal",datamaker,list(disttype="normal",nsamp=1000),1:100)
addScenario(dsc_eg,"uniform",datamaker,list(disttype="uniform",nsamp=1000),1:100)
addScenario(dsc_eg,"Cauchy",datamaker,list(disttype="Cauchy",nsamp=1000),seed=1:100)

###### Add Methods #####

addMethod(dsc_eg,"mean",mean.wrapper)
addMethod(dsc_eg,"median",median.wrapper)
addMethod(dsc_eg,"winsor",winsor.wrapper)

####### Define Score and Add it #######

score = function(data, output){
  return(list(squared_error = (data$meta$truemean-output$meanest)^2, 
              abs_error = abs(data$meta$truemean-output$meanest)))
}

addScore(dsc_eg,score)

######## Run the DSC #################

reset_dsc(dsc_eg,force=TRUE)
res=run_dsc(dsc_eg)
save(dsc_eg,file="dsc_eg.RData")

```

Now convert to BE and test a job and then run all jobs. 
```{r}
system("rm -r one_sample_location-files")

reg=dsc2BE(dsc_eg,"one_sample_location")
summarizeExperiments(reg)

id1 <- findExperiments(reg, algo.pattern="mean")[1]
testJob(reg,id1)


chunked <- chunk(getJobIds(reg), n.chunks = 10, shuffle = TRUE)
timetaken=system.time(submitJobs(reg, chunked))

res2=reduceResultsExperiments(reg, ids=findDone(reg))

```

Now compare results
```{r}
aggregate(squared_error~algo+prob,data=res2,mean)
aggregate(squared_error~method+scenario,res,mean)

aggregate(abs_error~algo+prob,data=res2,mean)
aggregate(abs_error~method+scenario,res,mean)

```

