---
title: "More Advanced: Using Parsers to Test Adaptive Shrinkage"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{More advanced demonstration of dscr}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(collapse = TRUE,comment = "#")
```

# More Advanced: Using Parsers to Test Adaptive Shrinkage

First we load the dscr package, as well as the ashr package used in
the example below.

```{r}
library(dscr)
library(ashr)
```

One original idea in introducing the DSC was to be very prescriptive
about input formats and output formats: all methods had to use the
same input and output formats.  In using the package in practice we
found that, particularly in more "exploratory" situations, where we
are in "research mode", it would be helpful to be less restrictive
about this.  Specifically, we wanted to be able to run a method on all
scenarios and store *all* of the output of each method, so that we
could later score the methods in multiple different ways.

To improve flexibility we implemented the idea of a parser to
post-process output. The idea is that the method wrappers can each
save in its preferred output format (e.g. the entire object produced
by whatever R function you are wrapping), and then you supply a
parser, or parsers, to convert this to another output format
(e.g. just one part of the entire object). Different output formats
are identified by different names (attribute `output_type`).  In
addition we implemented the possibility to have multiple scores, each
being used to score a specific `output_type`.

To illustrate we consider the problem of shrinkage, which is tackled
by the [`ashr` package](http://www.github.com/stephens999/ashr). The
input to this DSC is a set of estimates $\hat\beta$, with associated
standard errors $\s$. These values are estimates of actual (true)
values for $\beta$, so the meta-data in this case are the true values
of beta. Methods must take $\hat\beta$ and $s$ as input, and provide
as output "shrunk" estimates for $\beta$ (so output is a list with
one element, called beta_est, which is a vector of estimates for
beta). The score function then scores methods on their RMSE comparing
beta_est with beta.

First define a datamaker which simulates true values of $\beta$ from a
user-specified normal mixture, where one of the components is a point
mass at 0 of mass $\pi_0$, which is a user-specified parameter. It
then simulates $\hat\beta \sim N(\beta_j,s_j)$ (where $s_j$ is again
user-specified). It returns the true $\beta$ values and true $\pi_0$
value as meta-data, and the estimates $\hat\beta$ and $s$ as
input-data.

```{r}

#' @title datamaker for shrink DSC
#'
#' @description Simulates data for a DSC for methods to shrink
#'   estimates values.
#'
#' @details None
#' 
#' @param seed The seed for the pseudo-rng set before generating the
#'   parameters.
#' 
#' @param args A list of the remaining arguments, which in this case is:
#' 
#'   \item{nsamp}{The number of samples to create}
#' 
#'   \item{g}{An object of class normalmix specifying the mixture
#'     distribution from which non-null beta values are to be simulated.}
#' 
#'   \item{min_pi0}{The minimum value of pi0, the proportion of true nulls}
#' 
#'   \item{max_pi0}{The maximum value of pi0, the proportion of true null}
#' 
#'   \item{betahatsd}{The standard deviation of betahat to use}
#'
#' @return a list with the following elements:
#' 
#' \item{meta}{A list containing the meta data. In this case beta}
#' 
#' \item{input}{A list containing the input data; in this case the set
#'   of betahat values and their standard errors}
#' 
rnormmix_datamaker = function(args){
  
  # Here is the meat of the function that needs to be defined for each
  # dsc to be done.
  # 
  # Generate the proportion of true nulls randomly.
  pi0 = runif(1,args$min_pi0,args$max_pi0) 

  # Randomly draw a component.
  k = ncomp(args$g)
  comp = sample(1:k,args$nsamp,mixprop(args$g),replace=TRUE) 
  isnull = (runif(args$nsamp,0,1) < pi0)
  beta = ifelse(isnull, 0,rnorm(args$nsamp,comp_mean(args$g)[comp],
                comp_sd(args$g)[comp]))
  sebetahat = args$betahatsd
  betahat = beta + rnorm(args$nsamp,0,sebetahat)
  meta=list(beta=beta,pi0=pi0)
  input=list(betahat=betahat,sebetahat=sebetahat)
  
  # End of meat of function.
  data = list(meta=meta,input=input)
  
  return(data)
}
```

Now initialize the dsc using `new_dsc`, and add three scenarios using
this datamaker:

```{r}
# Initialize.
dsc_shrink = new_dsc("shrinkage","dsc-shrink-files")

# Add Scenarios.
add_scenario(dsc_shrink,name="An",
            fn=rnormmix_datamaker,
            args=list(
              g=normalmix(c(2/3,1/3),c(0,0),c(1,2)),
              min_pi0=0,
              max_pi0=1,
              nsamp=1000,
              betahatsd=1
            ),
            seed=1:2)

add_scenario(dsc_shrink,name="Bn",
            fn=rnormmix_datamaker,
            args=list(
              g=normalmix(rep(1/7,7),c(-1.5,-1,-0.5,0,0.5,1,1.5),rep(0.5,7)),
              min_pi0=0,
              max_pi0=1,
              nsamp=1000,
              betahatsd=1
            ),
            seed=1:2)

add_scenario(dsc_shrink,name="Cn",
            fn=rnormmix_datamaker,
            args=list(
              g=normalmix(c(1/4,1/4,1/3,1/6),c(-2,-1,0,1),c(2,1.5,1,1)),
              min_pi0=0,
              max_pi0=1,
              nsamp=1000,
              betahatsd=1
            ),
            seed=1:2)
```

Now define a method wrapper for the ash function from the `ashr`
package. Notice that this wrapper does not return output in the
required format - it simply returns the entire ash output.

```{r}
ash.wrapper=function(input,args=NULL){
  if(is.null(args)){
    args=list(mixcompdist="halfuniform",method="fdr")
  }
  res = do.call(ash, args=c(list(betahat = input$betahat,
                                 sebetahat = input$sebetahat),args))
  return(res)
}
```

When we add methods using the wrapper, we specify its outputtype:

```{r}
add_method(dsc_shrink,"ash.n",ash.wrapper,outputtype="ash_output",
           args=list(mixcompdist="normal"))
add_method(dsc_shrink,"ash.hu",ash.wrapper,outputtype="ash_output",
           args=list(mixcompdist="halfuniform"))
```

Now we can define a parser to convert the ash output to a simple list
with single element `beta_est`. Note that when we add this parser
function, we specify what the output type it is designed to convert
from (`ash_output`) and to (`est_output`):

```{r}
ash2beta_est =function(output){
  return (list(beta_est=output$PosteriorMean))
} 
add_output_parser(dsc_shrink,"ash2beta",ash2beta_est,
                  "ash_output","est_output")
```

When we add the score function we specify what outputtype it is
designed to use:

```{r}

# Define Score and Add it
score = function(data, output){
  return(list(RMSE=sqrt(mean((output$beta_est-data$meta$beta)^2))))
}
add_score(dsc_shrink,score,name="basicscore",outputtype="est_output")
```

Now we can run the DSC: it runs every method on every scenario, and
then every parser on all relevant output before running the scores:

```{r}
res1=run_dsc(dsc_shrink)
head(res1)
```

A nice feature is that we can now easily add an assessment of the
methods in another dimension. For example, we can look at accuracy of
estimates of the parameter $\pi_0$ by adding a parser and a
score. Effectively we have made 2 similar DSCs with the same methods
and input, but different output/scores/goals.  Note that the methods
have already been run, so they are not run again - only the parser and
scores are run this time. This feature could be particularly
convenient if the methods are computationally intensive.

Note: when a DSC has multiple scores the output is a list, with a
dataframe of results for each score.

```{r}
# This parser extracts the estimate of pi0.
ash2pi0 =function(output){
  return (list(pi0_est=get_pi0(output)))
} 
add_output_parser(dsc_shrink,"ash2pi0",ash2pi0,"ash_output","pi0_output")
score2 = function(data, output){
  return(list(pi0_est=output$pi0_est,pi0=data$meta$pi0))
}
add_score(dsc_shrink,score2,"pi0score",outputtype="pi0_output")
res2=run_dsc(dsc_shrink)
head(res2$pi0score)
head(res2$basicscore)
```
